Approximation as Differentiation: Notes

### 2025-05-25 main/category-of-families.tex
Less noisy notation for constant family.
Cleanup.

\begin{definition}[Category of families]
\label{def:Fam}
For any category $\cat{C}$ define $\Fam(\cat{C})$ to be the Grothendieck construction
$\Grothendieck{X}\Func{X}{\cat{C}}$.
\end{definition}

@@

We can verify that $\tangents$ is indeed a functor, regardless of whether the linear maps $\RR^m \linearto
\RR^n$ happen to be derivatives. But if $f_2(x)$ is the derivative of $f_1$ at $x$ for any $x \in \RR^m$ and
similarly for $g$ then the derivatives compose according to the forward chain rule and $(g \comp f)_2(x)$ is
the derivative of $(g \comp f)_1$ at $x$. We can see these maps as living in $\Fam(\FinVect)$ if we regard
every finite vector space $\RR^n$ as paired with the constant family of tangent spaces which is always $\RR^n$
(also written $\RR^n$, for convenience), and each map $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n)$ to
pairs $(f_1, f_2)$ as the pair of a differentiable function $f_1: \RR^m \to \RR^n$ and a family of linear maps
$f_2: \RR^m \to \RR^m \linearto \RR^n$.

>>>>

\begin{definition}[Categories of families]
\label{def:Fam}
For any category $\cat{C}$ define $\Fam(\cat{C})$ to be the Grothendieck construction
$\Grothendieck{X}\Func{X}{\cat{C}}$.
\end{definition}

@@

We can verify that $\tangents$ is indeed a functor, regardless of whether the linear maps $\RR^m \linearto
\RR^n$ happen to be derivatives. But if $f_2(x)$ is the derivative of $f_1$ at $x$ for any $x \in \RR^m$ and
similarly for $g$ then the derivatives compose according to the forward chain rule and $(g \comp f)_2(x)$ is
the derivative of $(g \comp f)_1$ at $x$. We can see these maps as living in $\Fam(\FinVect)$ if we regard
every finite vector space $\RR^n$ as paired with the constant family of tangent spaces which is always $\RR^n$
(also written $\RR^n$, for convenience), and each map $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n)$ as
the pair $(f_1, f_2)$ of a differentiable function $f_1: \RR^m \to \RR^n$ and family of linear maps $f_2:
\RR^m \to \RR^m \linearto \RR^n$.
